Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-07-17 manuscript/manuscript.tex
Minor changes in manuscript

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/tesseroid-uieda.pdf}
\caption{
A spherical prism, Tesseroid, in a geocentric spherical coordinate system, with a computation point $P$ and its local north oriented Cartesian coordinate system. Picture made by \citep{Uieda2015}.
}
\label{fig:tesseroid-uieda}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.9\linewidth]{figures/tesseroid-uieda.pdf}
\caption{
A spherical prism, also known as  Tesseroid, in a geocentric spherical coordinate system, with a computation point $P$ and its local north oriented Cartesian coordinate system. Picture made by \citep{Uieda2015}.
}
\label{fig:tesseroid-uieda}
\end{figure}
